---
title: "Walkthrough of the farsPackage in one minute"
author: "Yuanzhe Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This package provides convenient functions to extract, aggregate and
visualise the [Fatality Analysis Reporting System (FARS)](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars) data from the US National Highway Traffic Safety Administration, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


## Installation

You can install the package from GitHub using the `install_github` function from `devtools` as follows

```{r eval = FALSE}
library(devtools)
install_github("Roger-Li/farsPackage")
library(farsPackage)
```

## Load data from the package
```{r eval = FALSE}
data <- system.file("extdata", "accident_2013.csv.bz2", package = "farsPackage")
```

## Read data into a tibble.
```{r eval = FALSE}
library(dplyr)
library(readr)
df <- fars_read(data)
```

## Summarise data
The `fars_summarize_years` function reads in a vector of files and returns the # of observation by month and year
```{r eval=FALSE}
library(tidyr)
aggregated <- fars_summarize_years(c(2013, 2014, 2015))
```

## Map plot
`fars_map_state` function is used to draw observations as points on a map
```{r eval=FALSE}
library(maps)
library(graphics)
fars_map_state(48, 2015)
```

